Model-based variable selection for regression with highly correlated variables.

### 2014-05-19 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@608 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

	\subsection{Modeling the uncorrelated covariates: a full generative approach on $P(\boldsymbol{X})$} \label{sectionfullgen}
	To be able to compare structures with $P(S|\boldsymbol{X})$, we need a full generative model on $\boldsymbol{X}$. Sub-regressions give $P(\boldsymbol{X}_r|\boldsymbol{X}_f,S) $ but $P(\boldsymbol{X}_f|S)$ is still undefined. We suppose that variables in $\boldsymbol{X}_f$ follow Gaussian mixtures of $k_j \in \mathbf{N}^*$ components: 
	\begin{equation}
			\forall \boldsymbol{X}^j \notin \boldsymbol{X}_r : \boldsymbol{X}^j_{|S} \sim f(\boldsymbol{\theta}_j)=\mathcal{GM}(\boldsymbol{\pi}_j;\boldsymbol{\mu}_j;\boldsymbol{\sigma}^2_j) \textrm{ with } \boldsymbol{\pi}_j,\boldsymbol{\mu}_j,\boldsymbol{\sigma}^2_j \textrm{ vectors of size } K_j. \label{mixtureX1}
		\end{equation}
		The great flexibility \cite{mclachlan2004finite} of such models makes our model more robust. Gaussian case is just a special case ($K_j=1$) of Gaussian mixture so it is included in our hypothesis but identifiability of $S$ requires to have at least one Gaussian mixture with at least two distinct components in each sub-regression (derived from the identifiability of the SR model in \cite{maugis2009variable}, more details in the Appendices \ref{preuveident}).

@@

	When $n<p$, a frequently used method is the Moore-Penrose generalized inverse \cite{katsikis2008fast}, thus OLS can obtain some results even with $n<p$ (see tables \ref{YXlinOLS} and \ref{YX2linOLS} ).

@@

In table \ref{compZvrai} we compare found structures in different contexts with both Uniform and Hierarchical Uniform {\it a priori} law on $P(S)$, noted respectively $BIC$ and $BIC_+$. 
We see that usage of $BIC_+$ gives sparser models even with $\max (\hat{p}_f^j)=5$. Moreover, this constraint is not active because observed complexities are smaller (this constraint only serves to accelerate the walk by reducing the dimension of $\mathcal{S}$ because each configuration was computed a hundred times), meaning that the stronger penalty implied by $BIC_+$ really is efficient. The datasets used for $BIC$ and $BIC_+$ are the same to keep the comparison  meaningful. These datasets and $\hat{S}$ are those used for tables 
 \ref{YXlinOLS} to \ref{YX2linstep}.

@@

\clearpage
\subsubsection{$\boldsymbol{Y}$ depends only on covariates in $\boldsymbol{X_f}$ (best case for us)}	 \label{tableMSEsimgauche}
\begin{figure}[h!]
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/OLS_X1_MSE_NB.png} 
			\caption{Comparison of the MSE between OLS and CorReg+OLS}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/OLS_X1_compl_NB.png} 
			\caption{Comparison of the compexities between OLS and CorReg+OLS} 
   \end{minipage}
\end{figure}

>>>>

	\subsection{Modeling the uncorrelated covariates: a full generative approach on $P(\boldsymbol{X})$} \label{sectionfullgen}
	To be able to compare structures with $P(S|\boldsymbol{X})$, we need a full generative model on $\boldsymbol{X}$. Sub-regressions give $P(\boldsymbol{X}_r|\boldsymbol{X}_f,S) $ but $P(\boldsymbol{X}_f|S)$ is still undefined. We suppose that variables in $\boldsymbol{X}_f$ follow Gaussian mixtures of $k_j \in \mathbf{N}^*$ components: 
	\begin{equation}
			\forall \boldsymbol{X}^j \notin \boldsymbol{X}_r : \boldsymbol{X}^j_{|S} \sim f(\boldsymbol{\theta}_j)=\mathcal{GM}(\boldsymbol{\pi}_j;\boldsymbol{\mu}_j;\boldsymbol{\sigma}^2_j) \textrm{ with } \boldsymbol{\pi}_j,\boldsymbol{\mu}_j,\boldsymbol{\sigma}^2_j \textrm{ vectors of size } K_j. \label{mixtureX1}
		\end{equation}
		The great flexibility \cite{mclachlan2004finite} of such models makes our model more robust. Gaussian case is just a special case ($K_j=1$) of Gaussian mixture so it is included in our hypothesis but identifiability of $S$ requires to have Gaussian mixtures with at least two distinct components in each sub-regression (derived from the identifiability of the SR model in \cite{maugis2009variable}, more details in the Appendices \ref{preuveident}).

@@

	When $n<p$, a frequently used method is the Moore-Penrose generalized inverse \cite{katsikis2008fast}, thus OLS can obtain some results even with $n<p$. %(see tables \ref{YXlinOLS} and \ref{YX2linOLS} ).

@@

%In table \ref{compZvrai} 
We compare found structures in different contexts with both Uniform and Hierarchical Uniform {\it a priori} law on $P(S)$, noted respectively $BIC$ and $BIC_+$. 
We see that usage of $BIC_+$ gives sparser models even with $\max (\hat{p}_f^j)=5$. Moreover, this constraint is not active because observed complexities are smaller (this constraint only serves to accelerate the walk by reducing the dimension of $\mathcal{S}$ because each configuration was computed a hundred times), meaning that the stronger penalty implied by $BIC_+$ really is efficient. The datasets used for $BIC$ and $BIC_+$ are the same to keep the comparison  meaningful. %These datasets and $\hat{S}$ are used for   %tables \ref{YXlinOLS} to \ref{YX2linstep}.

@@

\clearpage
\subsubsection{$\boldsymbol{Y}$ depends only on covariates in $\boldsymbol{X_f}$ (best case for us)}	 \label{tableMSEsimgauche}
\begin{figure}[h!]
	\begin{minipage}[l]{.48\linewidth}
			\includegraphics[height=180px,width=245px]{figures/res_article/OLS_X1_MSE_NB.png} 
			\caption{Comparison of the MSE between OLS and CorReg+OLS}
	\end{minipage} \
   \begin{minipage}[r]{.48\linewidth}
			\includegraphics[height=180px,width=240px]{figures/res_article/OLS_X1_compl_NB.png} 
			\caption{Comparison of the complexities between OLS and CorReg+OLS} 
   \end{minipage}
\end{figure}
